Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features

### 2016-12-12 paper/responseToReviewers.tex

\item \emph{The argumentation toward the log compression is well conducted, and meaningful in this issue. The authors may simply swap the order of fig 3 and 4}

\item \emph{The class accuracy Table III for Home and Residential area are singular. Authors shall discuss that.}

\item \emph{Complete legend fig 5.}

The legend have been completed to help the readability of the figure.

@@

\end{enumerate}

\section{Responses to Reviewer 1}

\begin{enumerate}

\item \emph{Object-based is inappropriate, This paper introduces: no this paper uses the scattering network to try to tackle a specific sound classification task.}
The title has been changed to remove the "object-based" formulation. The particular approach introduced in the paper is the hierarchical representation of a scene as a partition of its distribution of scattering features. While the scattering transform, which has been introduced by previous works, forms the low-level layer of this representation, the hierarchical structure is novel and we believe generic enough to represent auditory scenes for a variety of information retrieval tasks.

\item \emph{The second paragraph of the abstract is vague.}
This paragraph has been reworded and worked into the rest of the abstract in a more fluid manner.

\item \emph{No novel technique is presented}
Again, the hierarchical representation proposed is novel and we provide adequate evidence, in our opinion, for its power in the proposed similarity retrieval task.

\item \emph{the whole paper architecture is poor}
Without any specific points of criticism, it is hard to address this particular statement.

### 2016-12-12 paper/structureScene.tex
Edit intro

This paper introduces a generic hierarchical modeling scheme for acoustic scenes using the wavelet scattering transform at sub-second time-scales with relevance-based quantization at larger time-scales. Instead of representing a scene using summary statistics, a method popularized by bag-of-features models, each scene is represented by a subset of its most representative features, allowing the retrieval system to focus on particular discriminative features in the scene. We demonstrate the potential of the proposed approach for both acoustic scene similarity retrieval and acoustic scene classification tasks on publicly available datasets, consistently outperforming baseline mel-frequency cepstral coefficient (MFCC) methods.

@@

\IEEEPARstart{T}{he} amount of audio data recorded from our sonic environment has grown considerably over the past decades.
In order to measure the effect of human activity and climate change on animal biodiversity, researchers in the field of ecoacoustics \cite{krause} have recently undertaken the massive deployment of acoustic sensors throughout the world \cite{warren2006urban, NessSST13, stowell13b}.

In addition, recent work demonstrates the interest of acoustic monitoring for the characterization of human pleasantness in urban areas \cite{guyot2005urban, ricciardi2015sound} as well as the prediction of annoyance due to traffic \cite{gloaguen}.
Because they bear a strong societal impact and raise many scientific challenges, we believe that these case studies are of considerable interest for the signal processing community.

Formally, ecoacoustics is the interdisciplinary study of natural and anthropogenic sounds and their relationship with the environment over a wide range of scales at the intersection between ecology, acoustics and computer science. Despite identified needs, the field of signal-based ecoacoustics is still in infancy.
As a consequence, few well-built datasets are readily available for evaluation purposes.

A closely related, and more mature, field of investigation is the classification of acoustic scenes, where the aim is to predict labels by processing audio data.
While narrower in its range of applications, it has the advantage of being rooted in cognitive psychology of categorization \cite{dubois2006cognitive, guastavino_ideal_2006} and has received the attention of the data mining community for some time, resulting in the availability of well-designed datasets.

Despite the differences, ecoacoustics and acoustic scene classification (ASC) task both raise the following question: how can we efficiently and effectively process a large amount of audio data using representations that are compact, generic in their design, and flexible in their use?

The work described in this paper attempts to answer this question by demonstrating the usefulness of two concepts: 1) using the wavelet scattering transform to extract discriminative features subject to a small number of parameters and 2) large time scale modeling of the acoustic scene based on unsupervised clustering of each acoustic scene, allowing us to hopefully focus the scene description on a few salient sound objects that carry most of the semantic information.

Motivations of the proposed approach and a brief review of the state of the art in the field of acoustic scene modeling is given in Section \ref{sec:soa}. We describe the scattering transform in Section \ref{sec:scattering}, discuss transformations of the resulting features in Section \ref{sec:design} and propose a cluster-based scene description in Section \ref{sec:object}. In Section \ref{sec:experiments}, several experiments are proposed for an unsupervised setting, acoustic scene similarity retrieval (ASSR), and for a supervised setting, acoustic scene classification (ASC). Results are subsequently reported in Section \ref{sec:results}.

>>>>

This paper introduces a generic hierarchical modeling scheme for acoustic scenes using the wavelet scattering transform at sub-second time-scales with relevance-based quantization at larger time-scales. Instead of representing a scene using summary statistics, a method popularized by bag-of-features models, each scene is represented by a subset of its most representative features, allowing the retrieval system to focus on discriminative features. We demonstrate the potential of the proposed approach for both acoustic scene similarity retrieval and acoustic scene classification tasks on publicly available datasets, consistently outperforming baseline mel-frequency cepstral coefficient (MFCC) methods.

@@

\IEEEPARstart{T}{he} amount of audio data recorded from our sonic environment has grown considerably over the past decades.
In order to measure the effect of human activity and climate change on animal biodiversity, researchers in the field of ecoacoustics \cite{krause} have recently undertaken the massive deployment of acoustic sensors throughout the world \cite{warren2006urban, NessSST13, stowell13b}. 
In addition, recent work has explored acoustic monitoring for characterization of human pleasantness in urban areas \cite{guyot2005urban, ricciardi2015sound}, as well as the prediction of annoyance due to traffic \cite{gloaguen}.
Because they bear a strong societal impact and raise many scientific challenges, we believe that these applications are of considerable interest for the signal processing community.

Ecoacoustics is the interdisciplinary study of relationships between natural or anthropogenic sounds and their environments at the intersection of ecology, acoustics and computer science. Despite identified needs, the field of signal-based ecoacoustics is still in its infancy.
As a consequence, few well-designed datasets are readily available for evaluation purposes.

A closely related, and more mature, field of investigation is the classification of acoustic scenes, where the aim is to predict labels by processing audio data.
While narrower in its range of applications, it has the advantage of being rooted in the cognitive psychology of categorization \cite{dubois2006cognitive, guastavino_ideal_2006} and has received the attention of the data mining community for some time, resulting in the availability of well-designed datasets.

Despite the differences, ecoacoustics and acoustic scene classification (ASC) task both raise the following question: how can we efficiently and effectively process a large amount of audio data using representations that are compact, generic in their design, and flexible in their use?
The work described in this paper attempts to answer this question by demonstrating the usefulness of two concepts: 1) application of the wavelet scattering transform to extract discriminative features and 2) large time-scale modeling of the acoustic scene based on unsupervised clustering of each acoustic scene, allowing us to focus the scene description on a few salient sound objects that carry most of the semantic information. \ja{Technically, the 1st concept has already been demonstrated in previous papers. Do we really want to claim this here?}

Motivations of the proposed approach and a brief review of the state of the art in the field of acoustic scene modeling is given in Section \ref{sec:soa}. We describe the scattering transform in Section \ref{sec:scattering}, discuss processing of the resulting features in Section \ref{sec:design} and propose a cluster-based scene description in Section \ref{sec:object}. In Section \ref{sec:experiments}, several experiments are proposed for the unsupervised setting of acoustic scene similarity retrieval (ASSR) and for the supervised setting of acoustic scene classification (ASC). Results are subsequently reported in Section \ref{sec:results}.
